### 2013-01-06 edupar-13/410.tex
Add syscall table

\subsubsection{Pebbles Kernel}
For the fourth project, two-student teams
implement a kernel which complies to the
same specification as the reference kernel
they previously relied on.
They implement some approach to
synchronizing and blocking threads while
they are in kernel space,
a simple round-robin scheduler,
basic virtual memory,
a program loader,
code to handle various x86 exceptions,
and code for setting up and tearing down
threads and processes.
Students re-use the basic device drivers
they implemented in the second project.
%% TODO Space permitting, maybe have a table of system calls?
%% The 410 section is otherwise lacking in visual aids. -- bblum
These ingredients are combined to yield
twenty-four system calls
(life-cycle, thread management, memory management,
console I/O, and miscellaneous).
%% TODO Justify by mentioning average lines of code. -- bblum
For most students in the class, this is the
largest and most complicated software artifact they
have produced.
%% TODO Huh? I don't get how the sentence below is supposed to flow.
%% Seems like it wants to elaborate on the concerns, but the next sentence
%% is different. -- bblum
Because the test suite and the grading criteria
emphasize robustness and preemptibility of
kernel code,
there are many cross-cutting concerns.
Because the students are responsible for ensuring
the run-time invariants underlying all compiler-generated
code in the system (kernel and user-space),
they gain experience with debugging at both the
``algorithm level'' and the register/bit-field level.

>>>>

\subsubsection{Pebbles Kernel}
For the fourth project, two-student teams
implement a kernel which complies to the
same specification as the reference kernel
they previously relied on.
They implement some approach to
synchronizing and blocking threads while
they are in kernel space,
a simple round-robin scheduler,
basic virtual memory,
a program loader,
code to handle various x86 exceptions,
and code for setting up and tearing down
threads and processes.
Students re-use the basic device drivers
they implemented in the second project.
%% TODO Space permitting, maybe have a table of system calls?
%% The 410 section is otherwise lacking in visual aids. -- bblum
These ingredients are combined to yield
twenty-five system calls
(life-cycle, thread management, memory management,
console I/O, and miscellaneous),
which are summarized in Figure~\ref{fig:syscalls}.
%% TODO Justify by mentioning average lines of code. -- bblum
For most students in the class, this is the
largest and most complicated software artifact they
have produced.
%% TODO Huh? I don't get how the sentence below is supposed to flow.
%% Seems like it wants to elaborate on the concerns, but the next sentence
%% is different. -- bblum
Because the test suite and the grading criteria
emphasize robustness and preemptibility of
kernel code,
there are many cross-cutting concerns.
Because the students are responsible for ensuring
the run-time invariants underlying all compiler-generated
code in the system (kernel and user-space),
they gain experience with debugging at both the
``algorithm level'' and the register/bit-field level.

\begin{figure}
	\center \footnotesize
	\begin{tabular}{|l|p{0.28\textwidth}|}
		\hline
		\bf System call name & \bf Summary \\
		\hline
		\multicolumn{2}{c}{\em Lifecycle management} \\
		\hline
		\x{fork} & Duplicates the invoking task, including all memory regions. \\
		\x{thread_fork} & Creates a new thread in the current task.\\
		\x{exec} & Replaces the program currently running in the invoking task with a new one specified. \\
		\x{set_status} & Records the exit status of the current task. \\
		\x{vanish} & Terminates execution of the calling thread. \\
		\x{wait} & Blocks execution until another task terminates, and collects its exit status.\\
		\x{task_vanish}* & Causes all threads of a task to \x{vanish}. \\
		\hline
		\multicolumn{2}{c}{\em Thread management} \\
		\hline
		\x{gettid} & Returns the ID of the invoking thread. \\
		\x{yield} & Defers execution to a specified thread. \\
		\x{deschedule} & Blocks execution of the invoking thread. \\
		\x{make_runnable} & Wakes up another \x{deschedule}d thread. \\
		\x{get_ticks} & Gets the number of timer ticks since bootup. \\
		\x{sleep} & Blocks a thread for a given number of ticks. \\
		\x{swexn} & Registers a given user-space function as a software exception handler.\\
		\hline
		\multicolumn{2}{c}{\em Memory management} \\
		\hline
		\x{new_pages} & Allocates a specified region of memory. \\
		\x{remove_pages} & Deallocates same. \\
		\hline
		\multicolumn{2}{c}{\em Console I/O} \\
		\hline
		\x{getchar}* & Reads one character from keyboard input. \\
		\x{readline} & Reads the next line from keyboard input. \\
		\x{print} & Prints a given memory buffer to the console. \\
		\x{set_term_color} & Sets the color for future console output. \\
		\x{set_cursor_pos} & Sets the console cursor location. \\
		\x{get_cursor_pos} & Retrieves the console cursor location. \\
		\hline
		\multicolumn{2}{c}{\em Miscellaneous} \\
		\hline
		\x{ls} & Loads a given buffer with the names of files stored in the RAM disk ``file system''. \\
		\x{halt} & Ceases execution of the operating system. \\
		\x{misbehave}* & Selects among several behaviors for thread interleaving in certain scenarios. \\
		\hline
	\end{tabular}
	\caption{The Pebbles specifcation defines 25 system calls. Students are not required to implement ones marked with an asterisk (*), though the reference kernel provides them. }
	\label{fig:syscalls}
\end{figure}
